Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-08-08 cover-letter.tex
cover letter

\documentclass{letter}
\usepackage{graphics}
\usepackage{fullpage}
\topmargin=-0.2in
%\headheight=0in
\setlength\oddsidemargin{-0.2in}
\textheight=8.5in
\textwidth=7in
\def\apl#1#2{
\begin{letter}{#1}
\signature{Mahbubul Majumder, Heike Hofmann and Dianne Cook\\Department of Statistics\\Iowa State University 
\\Ames, Iowa 50011-1210\\ Phone (515) 294 3440\\{\tt mahbub@iastate.edu}}
\opening{{Dear #2,}}

@@

Since theory and methods section of the journal publishes graphical
methods in statistics, we believe it is a potentially interesting
paper for the JASA readership. One concern we have is that would be
considered to be long by JASA standards (28 pages, single spacing) and
we would not find it easy to shorten it.

@@

{{\pdfimage width 4in {letterhead.jpg}}}
\apl{Professor Xuming He \\Theory and Methods Editor\\Journal of American Statistical Association}{Professor He}

>>>>

\documentclass{letter}
\usepackage{graphics}
\usepackage{fullpage}
\topmargin=-0.2in
%\headheight=0in
\setlength\oddsidemargin{-0.2in}
\textheight=8.5in
\textwidth=7in
\def\apl#1#2{
\begin{letter}{#1}
\signature{Mahbubul Majumder\\
with Heike Hofmann and Dianne Cook\\Department of Statistics\\Iowa State University 
\\Ames, Iowa 50011-1210\\ Phone (515) 294 3440\\{\tt mahbub@iastate.edu}}
\opening{{Dear #2,}}

@@

The JASA instructions for authors say

\begin{quote}
``Authors are reminded that, although statistical theory has roots in mathematics, the phrase theory and methods should be interpreted broadly to include all techniques relevant to statistics and probability. This may include computational and graphical methods as well as more traditional mathematical methods.''
\end{quote}
We believe this paper is of interest to  the JASA readership. One concern we have is that it may be
considered to be long by JASA standards (28 pages, single spacing) and
we would not find it easy to shorten it.

@@

{{\pdfimage width 4in {letterhead.jpg}}}
\apl{Professor Xuming He and Jun Liu\\Theory and Methods Editors\\Journal of American Statistical Association}{Professors He and Liu}
